---
title: "Confirmatory Data Analysis"
author: "Michael Djohan"
date: 11 Mar 2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
format: html
editor: visual
---

## 1. Installing and launching the required R packages

```{r}
pacman::p_load("tmap", "ExPanDaR", "kableExtra", "ggstatsplot", "plotly", "DT", "scales","tidyverse", "rlang")
```

## 2. Loading the data

```{r}
touristdata_clean <- read_csv("data/touristdata_clean.csv")
```

### 2.1 Adding cost per pax

```{r}
touristdata_clean <- touristdata_clean %>%
  filter(total_cost > 0,
         total_tourist > 0,
         total_night_spent > 0) %>%
  mutate(cost_per_pax = round(total_cost/total_tourist,0),
         cost_per_night = round(total_cost/total_night_spent,0),
         cost_per_pax_night = round(total_cost/total_tourist/total_night_spent,0))
```

## 3. Data overview

### 3.1 Desriptive Statistics

```{r}
descr <- prepare_descriptive_table(touristdata_clean %>%
                                       select(!c(14,15,16,17,18,19,20,26))
                                   ) 


datatable(descr$df, class= "hover") %>%
  formatRound(column = c("Mean", "Std. dev.", "Median"), digits=2)
```

### 3.2 Distribution of numerical variables

```{r}
plot <- touristdata_clean %>% 
  select(c(7,8,9,21,22,23,24,28,29,30,31)) %>% 
  gather() %>%
  ggplot(aes(value)) +
  facet_wrap( ~key, ncol=4, scales="free") +
  geom_histogram()

ggplotly(plot)
```

Note:

1.  Majority spent on mainland
2.  Mostly travel \<5 people
3.  Spent 5 days on median

### 3.3 Distribution of categorical variables

```{r}
#| fig-height: 20
#| fig-width: 10
plot <- touristdata_clean %>% 
  select(c(3,5,6,10,11,12,13,14,15,16,17,18,19,20,25,26,27)) %>% 
  gather() %>%
  ggplot(aes(value)) +
  facet_wrap( ~key, ncol=3, scales="free") +
  geom_bar()

ggplotly(plot)
```

Note:

1.  Many younger tourist (25-44)
2.  Info mainly comes from friends and travel agents
3.  Many comes for wildlife tourism and beach tourism
4.  Many European and African Tourists
5.  Many travel alone
6.  Many comes for leisure and holidays

## 4. Exploring by Regions and Countries

### 4.1 Plotting the choropleth map for aggregated metrics

The object World is a spatial object of class sf from the sf package; it is a data.frame with a special column that contains a geometry for each row, in this case polygons

Reference - https://cran.r-project.org/web/packages/tmap/vignettes/tmap-getstarted.html

```{r}
data("World")
```

```{r}
touristdata_clean_country <- touristdata_clean %>%
  group_by(country,code,region) %>%
  summarise(total_female = sum(total_female),
            total_male = sum(total_male),
            total_tourist = sum(total_tourist),
            total_cost = round(sum(total_cost),0),
            total_night_spent = round(sum(total_night_spent),0),
            cost_per_pax = round(mean(cost_per_pax),0),
            cost_per_night = round(mean(cost_per_night),0),
            cost_per_pax_night = round(mean(cost_per_pax_night),0),
            trips = n()) %>%
  mutate(avg_night_spent = round(total_night_spent/trips,0)) %>%
  ungroup()
```

Joining the two dataframes together

```{r}
touristdata_clean_map <- left_join(World, 
                                 touristdata_clean_country, 
                          by = c("iso_a3" = "code")) %>%
  select(-c(2:15)) %>%
  na.omit()
```

```{r}
plot_map_eda <- function(metric = "total_tourist", style = "jenks", classes = 5, minvisitors = 30){

metric_text = case_when(metric == "total_female" ~ "Number of Female Visitors",
                        metric == "total_male" ~ "Number of Male Visitors",
                        metric == "total_tourist" ~ "Number of Visitors",
                        metric == "total_cost" ~ "Total Spending (TZS)",
                        metric == "cost_per_pax" ~ "Average Individual Spending (TZS)",
                        metric == "cost_per_night" ~ "Average Spending per Night (TZS)",
                        metric == "cost_per_pax_night" ~ "Average Individual Spending per Night (TZS)")
  
tmap_mode("view")

tm_shape(touristdata_clean_map %>%
           filter(total_tourist >= minvisitors))+
  tm_fill(metric, 
          n = classes,
          style = style, 
          palette="YlGn", 
          id = "country",
          title = metric_text
          ) +
  
  tm_borders(col = "grey20",
             alpha = 0.5) 

}
```

```{r}
plot_map_eda(metric = "cost_per_pax_night", style = "jenks", classes = 6, minvisitors = 20)
```

Note:

1.  Majority of tourists come from US, Western Europe, and South Africa
2.  Many outliers in individual average spending, so only focus on countries with at least 20 visitors, then it's revealed that Australians spend the highest, followed by Americans and Canadians.

### 4.2 CDA by Regions

#### 4.2.1 For Numerical Variables

```{r}
plot_ANOVA_region <- function(metric = "cost_per_pax_night", minvisitors = 30, testtype = "np", pair = "ns", compare = T, conf = 0.95, nooutliers = T) {
  
metric_text = case_when(metric == "total_female" ~ "Number of Female Visitors",
                        metric == "total_male" ~ "Number of Male Visitors",
                        metric == "total_tourist" ~ "Number of Visitors",
                        metric == "total_cost" ~ "Total Spending (TZS)",
                        metric == "cost_per_pax" ~ "Individual Spending (TZS)",
                        metric == "cost_per_night" ~ "Spending per Night (TZS)",
                        metric == "cost_per_pax_night" ~ "Individual Spending per Night (TZS)",
                        metric == "prop_night_spent_mainland" ~ "Proportion of Night spent in Mainland Tanzania",
                        TRUE ~ metric)

paratext <- case_when(testtype == "p" ~ "Mean (Parametric)",
                      testtype == "np" ~ "Median (Non-Parametric)",
                      testtype == "r" ~ "Mean (Robust t-test)",
                      testtype == "bayes" ~ "Mean (Bayesian)",
                      )

touristdata_countrylist <- touristdata_clean_country %>%
  filter(total_tourist >= minvisitors)

countrylist <- unique(touristdata_countrylist$country)

touristdata_ANOVA <- touristdata_clean %>%
  filter(country %in% countrylist) %>%
  mutate(region = fct_reorder(region, !!sym(metric), median, .desc = TRUE)) %>%
  drop_na()

if(nooutliers == T){
  touristdata_ANOVA <- touristdata_ANOVA %>%
      treat_outliers() 
}

touristdata_ANOVA %>% 
  ggbetweenstats(x = region, y = !!sym(metric),
                 xlab = "Region", ylab = metric_text,
                 type = testtype, pairwise.comparisons = T, pairwise.display = pair, 
                 mean.ci = T, p.adjust.method = "fdr",  conf.level = conf,
                 title = paste0("Comparison of ",paratext," ",metric_text, " across Regions"),
                 package = "ggthemes", palette = "Tableau_10")

}
```

```{r}
plot_ANOVA_region(metric = "cost_per_pax_night", minvisitors = 30, testtype = "np", pair = "ns", compare = T, conf = 0.95, nooutliers = T)
```

Note: Outliers can be treated Ability to exclude countries with less than minvisitors limit

1.  Oceania visitors spend the most while African visitors tends to spend the least

```{r}
plot_ANOVA_region(metric = "prop_night_spent_mainland", minvisitors = 30, testtype = "np", pair = "ns", conf = 0.95)
```

Note : European customers spend more time in Zanzibar

#### 4.2.2 For Categorical Variables

```{r}
plot_barstats_region <- function(metric = "purpose", minvisitors = 30, testtype = "np",conf = 0.95) {
  
metric_text = case_when(metric == "age_group" ~ "Age Group",
                        metric == "travel_with" ~ "Travelling Companion",
                        metric == "purpose" ~ "Purpose",
                        metric == "main_activity" ~ "Main Activity",
                        metric == "info_source" ~ "Source of Information",
                        metric == "tour_arrangement" ~ "Tour Arrangement",
                        metric == "package_transport_int" ~ "Include International Transportation?",
                        metric == "package_accomodation" ~ "Include accomodation service?",
                        metric == "package_food" ~ "Include food service?",
                        metric == "package_transport_tz" ~ "Include domestic transport service?",
                        metric == "package_sightseeing" ~ "Include sightseeing service?",
                        metric == "package_guided_tour" ~ "Include guided tour?",
                        metric == "package_insurance" ~ "Insurance Included?",
                        metric == "payment_mode" ~ "Mode of Payment",
                        metric == "first_trip_tz" ~ "First trip to Tanzania?",
                        metric == "most_impressing" ~ "Most impressive about Tanzania?",
                        TRUE ~ metric)

touristdata_countrylist <- touristdata_clean_country %>%
  filter(total_tourist >= minvisitors)

countrylist <- unique(touristdata_countrylist$country)

touristdata_barstats <- touristdata_clean %>%
  filter(country %in% countrylist) %>%
  drop_na()

touristdata_barstats %>% 
  ggbarstats(x = !!sym(metric), y = region,
             xlab = "Region", legend.title = metric_text,
             type = testtype, conf.level = conf,
             palette = "Set2")

}
```

```{r}
plot_barstats_region(metric = "travel_with", minvisitors = 30, testtype = "np", conf = 0.95)
```

```{r}
plot_barstats_region(metric = "purpose", minvisitors = 30, testtype = "np", conf = 0.95)
```

```{r}
plot_barstats_region(metric = "package_insurance", minvisitors = 30, testtype = "np", conf = 0.95)
```

```{r}
plot_barstats_region(metric = "first_trip_tz", minvisitors = 30, testtype = "np", conf = 0.95)
```

### 4.3 CDA by Selected Countries

Examining the largest spender by country

```{r}
touristdata_clean_country_sorted <- touristdata_clean_country %>%
  filter(total_cost > 0,
         total_tourist >= 60) %>%
  arrange(desc(cost_per_pax_night))

top8 <- touristdata_clean_country_sorted$country[1:8]

touristdata_clean_country_sorted
```

#### 4.3.1 For Numerical Variables

```{r}
plot_ANOVA_country <- function(metric = "cost_per_pax_night", selected_countries, testtype = "np", pair = "ns", compare = T, conf = 0.95, nooutliers = T) {
  
metric_text = case_when(metric == "total_female" ~ "Number of Female Visitors",
                        metric == "total_male" ~ "Number of Male Visitors",
                        metric == "total_tourist" ~ "Number of Visitors",
                        metric == "total_cost" ~ "Total Spending (TZS)",
                        metric == "cost_per_pax" ~ "Individual Spending (TZS)",
                        metric == "cost_per_night" ~ "Spending per Night (TZS)",
                        metric == "cost_per_pax_night" ~ "Individual Spending per Night (TZS)",
                        metric == "prop_night_spent_mainland" ~ "Proportion of Night spent in Mainland Tanzania",
                        TRUE ~ metric)

paratext <- case_when(testtype == "p" ~ "Mean (Parametric)",
                      testtype == "np" ~ "Median (Non-Parametric)",
                      testtype == "r" ~ "Mean (Robust t-test)",
                      testtype == "bayes" ~ "Mean (Bayesian)",
                      )

touristdata_ANOVA <- touristdata_clean %>%
  filter(country %in% selected_countries) %>%
  mutate(country = fct_reorder(country, !!sym(metric), median, .desc = TRUE)) %>%
  drop_na()

if(nooutliers == T){
  touristdata_ANOVA <- touristdata_ANOVA %>%
      treat_outliers() 
}

touristdata_ANOVA %>% 
  ggbetweenstats(x = country, y = !!sym(metric),
                 xlab = "Country", ylab = metric_text,
                 type = testtype, pairwise.comparisons = compare, pairwise.display = pair, 
                 mean.ci = T, p.adjust.method = "fdr",  conf.level = conf,
                 title = paste0("Comparison of ",paratext," ",metric_text, " across Countries"),
                 package = "ggthemes", palette = "Tableau_10")

}
```

```{r}
plot_ANOVA_country(metric = "cost_per_pax_night", selected_countries = top8, testtype = "np", pair = "ns", compare = F, conf = 0.95, nooutliers = T)
```

Majority of big spender indeed comes from Australia, followed by US, Canada, New Zealand, Denmark, and South Africa. However, it is noted that there is no statistically significant difference among many of them

```{r}
plot_ANOVA_country(metric = "prop_night_spent_mainland", selected_countries = top8, testtype = "np", pair = "ns", conf = 0.95)
```

#### 4.3.2 For Categorical Variables

```{r}
plot_barstats_country <- function(metric = "purpose", selected_countries, testtype = "np",conf = 0.95) {
  
metric_text = case_when(metric == "age_group" ~ "Age Group",
                        metric == "travel_with" ~ "Travelling Companion",
                        metric == "purpose" ~ "Purpose",
                        metric == "main_activity" ~ "Main Activity",
                        metric == "info_source" ~ "Source of Information",
                        metric == "tour_arrangement" ~ "Tour Arrangement",
                        metric == "package_transport_int" ~ "Include International Transportation?",
                        metric == "package_accomodation" ~ "Include accomodation service?",
                        metric == "package_food" ~ "Include food service?",
                        metric == "package_transport_tz" ~ "Include domestic transport service?",
                        metric == "package_sightseeing" ~ "Include sightseeing service?",
                        metric == "package_guided_tour" ~ "Include guided tour?",
                        metric == "package_insurance" ~ "Insurance Included?",
                        metric == "payment_mode" ~ "Mode of Payment",
                        metric == "first_trip_tz" ~ "First trip to Tanzania?",
                        metric == "most_impressing" ~ "Most impressive about Tanzania?",
                        TRUE ~ metric)


touristdata_barstats <- touristdata_clean %>%
  filter(country %in% selected_countries) %>%
  drop_na()

touristdata_barstats %>% 
  ggbarstats(x = !!sym(metric), y = country,
             xlab = "Country", legend.title = metric_text,
             type = testtype, conf.level = conf,
             palette = "Set2")

}
```

```{r}
plot_barstats_country(metric = "travel_with", selected_countries = top8, testtype = "np", conf = 0.95)
```

```{r}
plot_barstats_country(metric = "purpose", selected_countries = top8, testtype = "np", conf = 0.95)
```

```{r}
plot_barstats_country(metric = "package_insurance", selected_countries = top8, testtype = "np", conf = 0.95)
```

```{r}
plot_barstats_country(metric = "first_trip_tz", selected_countries = top8, testtype = "np", conf = 0.95)
```

## 5. Exploring Spending vs Other Variables

### 5.1 For Numerical Variables

```{r}
plot_scatter <- function(xaxis = "prop_night_spent_mainland", yaxis = "cost_per_pax_night", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), max_xaxis, testtype = "np", conf = 0.95, nooutliers = T) {
  
xaxis_text = case_when(xaxis == "total_female" ~ "Number of Female Visitors",
                       xaxis == "total_male" ~ "Number of Male Visitors",
                       xaxis == "total_tourist" ~ "Number of Visitors",
                       xaxis == "prop_night_spent_mainland" ~ "Proportion of Night spent in Mainland Tanzania",
                       xaxis == "total_night_spent" ~ "Total Night Spent",
                       TRUE ~ xaxis)

yaxis_text = case_when(yaxis == "total_cost" ~ "Total Spending (TZS)",
                       yaxis == "cost_per_pax" ~ "Individual Spending (TZS)",
                       yaxis == "cost_per_night" ~ "Spending per Night (TZS)",
                       yaxis == "cost_per_pax_night" ~ "Individual Spending per Night (TZS)",
                       TRUE ~ yaxis)

if(nooutliers == T){
  touristdata_clean <- touristdata_clean %>%
      treat_outliers() 
}

touristdata_clean %>%
  filter(region %in% regionlist,
         !!sym(xaxis) <= max_xaxis) %>%
  ggscatterstats(x = !!sym(xaxis), y = !!sym(yaxis),
                 type = testtype, conf.level = conf) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(x = xaxis_text, y = yaxis_text)
  
}
```

```{r}
plot_scatter(xaxis = "total_tourist", yaxis = "total_cost", regionlist = c("Europe","Americas","Oceania"), max_xaxis = 100, testtype = "np", conf = 0.95, nooutliers = T)
```

### 5.2 For Categorical Variables

```{r}
plot_ANOVA <- function(xaxis = "age_group", yaxis = "total_cost", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np", pair = "ns",conf = 0.95, nooutliers = T) {
  
xaxis_text = case_when(xaxis == "age_group" ~ "Age Group",
                        xaxis == "travel_with" ~ "Travelling Companion",
                        xaxis == "purpose" ~ "Purpose",
                        xaxis == "main_activity" ~ "Main Activity",
                        xaxis == "info_source" ~ "Source of Information",
                        xaxis == "tour_arrangement" ~ "Tour Arrangement",
                        xaxis == "package_transport_int" ~ "Include International Transportation?",
                        xaxis == "package_accomodation" ~ "Include accomodation service?",
                        xaxis == "package_food" ~ "Include food service?",
                        xaxis == "package_transport_tz" ~ "Include domestic transport service?",
                        xaxis == "package_sightseeing" ~ "Include sightseeing service?",
                        xaxis == "package_guided_tour" ~ "Include guided tour?",
                        xaxis == "package_insurance" ~ "Insurance Included?",
                        xaxis == "payment_mode" ~ "Mode of Payment",
                        xaxis == "first_trip_tz" ~ "First trip to Tanzania?",
                        xaxis == "most_impressing" ~ "Most impressive about Tanzania?",
                        TRUE ~ xaxis)

yaxis_text = case_when(yaxis == "total_cost" ~ "Total Spending (TZS)",
                       yaxis == "cost_per_pax" ~ "Individual Spending (TZS)",
                       yaxis == "cost_per_night" ~ "Spending per Night (TZS)",
                       yaxis == "cost_per_pax_night" ~ "Individual Spending per Night (TZS)",
                       TRUE ~ yaxis)


touristdata_ANOVA <- touristdata_clean %>%
  filter(region %in% regionlist) %>%
  drop_na()

if(nooutliers == T){
  touristdata_ANOVA <- touristdata_ANOVA %>%
      treat_outliers() 
}

touristdata_ANOVA %>% 
  ggbetweenstats(x = !!sym(xaxis), y = !!sym(yaxis),
                 xlab = xaxis_text, ylab = yaxis_text,
                 type = testtype, pairwise.comparisons = T, pairwise.display = pair, 
                 mean.ci = T, p.adjust.method = "fdr",  conf.level = conf,
                 package = "ggthemes", palette = "Tableau_10")

}
```

```{r}
plot_ANOVA(xaxis = "travel_with", yaxis = "total_cost", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np", pair = "ns",conf = 0.95, nooutliers = T)
```

```{r}
plot_ANOVA(xaxis = "age_group", yaxis = "total_cost", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np", pair = "ns",conf = 0.95)
```

```{r}
plot_ANOVA(xaxis = "purpose", yaxis = "total_cost", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np", pair = "ns",conf = 0.95)
```

## 6. Exploring Other Variables

```{r}
plot_barstats <- function(xaxis = "age_group", yaxis = "purpose", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np",conf = 0.95) {
  
xaxis_text = case_when(xaxis == "age_group" ~ "Age Group",
                        xaxis == "travel_with" ~ "Travelling Companion",
                        xaxis == "purpose" ~ "Purpose",
                        xaxis == "main_activity" ~ "Main Activity",
                        xaxis == "info_source" ~ "Source of Information",
                        xaxis == "tour_arrangement" ~ "Tour Arrangement",
                        xaxis == "package_transport_int" ~ "Include International Transportation?",
                        xaxis == "package_accomodation" ~ "Include accomodation service?",
                        xaxis == "package_food" ~ "Include food service?",
                        xaxis == "package_transport_tz" ~ "Include domestic transport service?",
                        xaxis == "package_sightseeing" ~ "Include sightseeing service?",
                        xaxis == "package_guided_tour" ~ "Include guided tour?",
                        xaxis == "package_insurance" ~ "Insurance Included?",
                        xaxis == "payment_mode" ~ "Mode of Payment",
                        xaxis == "first_trip_tz" ~ "First trip to Tanzania?",
                        xaxis == "most_impressing" ~ "Most impressive about Tanzania?",
                        TRUE ~ xaxis)

yaxis_text = case_when(yaxis == "age_group" ~ "Age Group",
                        yaxis == "travel_with" ~ "Travelling Companion",
                        yaxis == "purpose" ~ "Purpose",
                        yaxis == "main_activity" ~ "Main Activity",
                        yaxis == "info_source" ~ "Source of Information",
                        yaxis == "tour_arrangement" ~ "Tour Arrangement",
                        yaxis == "package_transport_int" ~ "Include International Transportation?",
                        yaxis == "package_accomodation" ~ "Include accomodation service?",
                        yaxis == "package_food" ~ "Include food service?",
                        yaxis == "package_transport_tz" ~ "Include domestic transport service?",
                        yaxis == "package_sightseeing" ~ "Include sightseeing service?",
                        yaxis == "package_guided_tour" ~ "Include guided tour?",
                        yaxis == "package_insurance" ~ "Insurance Included?",
                        yaxis == "payment_mode" ~ "Mode of Payment",
                        yaxis == "first_trip_tz" ~ "First trip to Tanzania?",
                        yaxis == "most_impressing" ~ "Most impressive about Tanzania?",
                        TRUE ~ yaxis)


touristdata_barstats <- touristdata_clean %>%
  filter(region %in% regionlist) %>%
  drop_na()

touristdata_barstats %>% 
  ggbarstats(x = !!sym(yaxis), y = !!sym(xaxis),
             xlab = xaxis_text, legend.title = yaxis_text,
             type = testtype, conf.level = conf,
             palette = "Set2")

}
```

```{r}
plot_barstats(xaxis = "age_group", yaxis = "purpose", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np",conf = 0.95)
```

```{r}
plot_barstats(xaxis = "main_activity", yaxis = "tour_arrangement", regionlist = c("Asia", "Africa", "Europe", "Oceania", "Americas"), testtype = "np",conf = 0.95)
```

## 7. Exploring alternative plotting of scatterplot

Due to issues with plots using the ggscatterstats function not appearing on the app correctly, we explored an alternative way of plotting the chart without using the ggstatsplot package. This alternative method makes use of geom_smooth to draw the trend line and the stats package to compute the correlation estimates and p-values.

```{r}
scatter_labeller <- function(col_name, test_type, conf_level) {
  filter_list <- touristdata_clean %>%
  select(!!sym(col_name)) %>%
  distinct()
  
  numrows <- as.numeric(length(filter_list[[1]]))
  
  est_score <- c()
  p_score <- c()
  
  for (n in range(1:numrows)){
    filter_char <-  as.character(filter_list[n,])

    filter_df <- touristdata_clean %>%
      filter(!!sym(col_name) == filter_char)
  
    corscore <- cor.test(filter_df$cost_per_pax,
                    filter_df$total_night_spent,
                    method = test_type, exact = F, 
                    conf.level = conf_level)
    
    est_score <- append(est_score, corscore$estimate)
    p_score <- append(p_score, corscore$p.value)
  }
  
  new_df <- data.frame(matrix(ncol=3,nrow=0, 
                              dimnames=list(NULL, 
                                            c(col_name, "est_score", "p_score"))))
  
  new_df <- cbind(filter_list, data.frame(est_score), data.frame(p_score), 
                  row.names = NULL)
  
  correl_label <- paste0("\n ", test_type, " correlation: ", 
                         round(new_df[[2]],3),
                         "\np-value: ", round(new_df[[3]],3))

  appender <- function(string, suffix = correl_label) paste0(string, suffix)
  
  return(appender)
}

```

```{r}
facet_labels <- scatter_labeller("travel_with", "spearman", 0.95)
```

```{r}
options(scipen = 999)
ggplot(touristdata_clean, aes(x = cost_per_pax, y = total_night_spent)) +
  geom_point() + geom_smooth(method = "lm") + 
  facet_grid(~travel_with, labeller = as_labeller(facet_labels)) + 
  labs(x = "Cost per Pax (TZS)", y = "Total Nights Spent")
```
